\section{Introduction} \label{sec:introduction}
Authorship verification is the process of verifying the authorship of a text.
You are given a set of texts known to be written by the author and an unknown
text that has to be classified as either written by the author or someone else.
The normal approach to the problem is to use stylometry to extract features from
the text and then some form of machine learning or statistical method to analyse
the data \cite{stamatos2009}. Many different text features have been proposed
to describe an author's writing style. That includes, but is not limited to,
character frequencies, word frequencies, vocabulary size, sentence length,
punctuation usage, character n-grams, word n-grams and \gls{POS}-tagging n-grams
\cite{stamatos2009}.

Authorship verification has been used for plagiarism control in danish secondary
schools \cite{hansen2014} and also has uses in civil law, criminal law and
computer forensics \cite{stamatos2009}.

In this article we explore state-of-the-art methods for authorship verification.
We extract several different types of features including word frequencies, word
n-grams and \gls{POS}-tagging n-grams. We implement several different algorithms
to work on the features. We start by implementing a baseline method which is a
distance based approach in which an unknown text is considered to be written
by the closest author. We then use the baseline method to compare to our other
results. We use data from two sources \cite{pan:2015} and \cite{pan:2013} which
are two instances of a yearly competition in digital text forensics. Since we
use the data from those two competitions we also compare our results to the
results obtained by others in the competition.
